Self Regulation Ontology Retest Data Report

### 2018-01-18 code/SRO_Report.Rmd
updating report for draft

calc_break_dvs = function(x, breaks=seq(0, 360, 10)[-1]){
  out = data.frame()
  for(i in 1:length(breaks)){
    tmp = x[1:breaks[i],]
    dvs = tmp %>%
      summarise(acc = mean(correct),
                avg_rt = median(rt[correct == 1]),
                score = sum(correct))
    out = rbind(out, dvs)
  }
  return(out)
}

tmp = t1_hr%>% filter(worker_id == 's005')

calc_break_dvs(tmp)

t1_hr %>%
  group_by(worker_id) %>%
  summarise(acc = mean(correct),
                avg_rt = median(rt[correct == 1]),
                score = sum(correct))
```

>>>>

calc_break_dvs = function(x, breaks=seq(0, 360, 10)[-1]){

  calc_dvs = function(x){
    out = x %>%
      summarise(acc = mean(correct),
                avg_rt = median(rt[correct == 1]),
                score = sum(correct))
    return(out)
  }

  out = data.frame()

  for(i in 1:length(breaks)){
    tmp = x[1:breaks[i],]
    dvs = calc_dvs(tmp)
    out = rbind(out, dvs)
  }

  # due to timeout trials exclusion not all subjects might have 360 rows
  # this would lead to na's for later trial breaks
  # first remove these
  out = out %>% drop_na()

  # then calculate the dv's for the remaining trials
  if(nrow(x)!=360 & nrow(x)%%10 != 0){
    dvs = calc_dvs(x)
    out = rbind(out, dvs)
  }

  #to keep track for later merge
  out$breaks = row.names(out)

  return(out)
}

#get dv's for t1 and t2
t1_dvs = t1_hr %>%
  group_by(worker_id) %>%
  do(calc_break_dvs(.))

t2_dvs = t2_hr %>%
  group_by(worker_id) %>%
  do(calc_break_dvs(.))

# merge to get same number of rows for each subject at both time points
hr_merge = merge(t1_dvs, t2_dvs, by = c("worker_id", "breaks"))

rm(t1_dvs, t2_dvs)

hr_merge = hr_merge %>%
  gather(key, value, -worker_id, -breaks) %>%
  separate(key, c("dv", "time"), sep="\\.") %>%
  mutate(time = ifelse(time == "x", 1, 2)) %>%
  arrange(worker_id, time, as.numeric(breaks))

hr_merge %>% 
  spread(dv, value) %>%
  group_by(breaks) 
# calculate point estimates for reliability

tmp = hr_merge %>% 
  spread(dv, value) %>%
  filter(breaks == 30) %>%
  select(time, acc)

ICC(tmp)$results['Average_fixed_raters', 'ICC']

hr_merge
```
